API design for machine learning software: experiences from the scikit-learn project

### 2013-08-09 paper.tex
Feature extraction are implemented as transformers as well
Cite Orange

Since it is common to modify or filter data before feeding it to a learning
algorithm, some estimators in the library implement a \textit{transformer}
interface which defines a \texttt{transform} method. It takes as input some new
data \texttt{X\_test} and yields as output a transformed version of
\texttt{X\_test}. Preprocessing, feature selection and dimensionality reduction
algorithms are all provided as transformers within the library.  In our example,
to standardize the input \texttt{X\_train} to zero mean and unit variance
before fitting the logistic regression estimator,
one would write:
\begin{pythoncode}
from sklearn.preprocessing import StandardScaler

@@

Recent years have witnessed a rising interest in machine learning and data mining
with applications in many fields.
With this rise comes a host of machine learning packages
(both open source and proprietary) with which \sklearn competes.
Although it can also be used through its Java API, Weka \citep{hall2009weka} is
popularly used through its graphical user interface (GUI). The target audience
of \sklearn is capable of programming, and therefore we focus on developing
a usable and consistent API, rather than expend effort into creating a GUI\@. In
addition, running machine learning through a GUI makes reproducibility difficult
(although Weka has developed a GUI for managing such workflows).

>>>>

Since it is common to modify or filter data before feeding it to a learning
algorithm, some estimators in the library implement a \textit{transformer}
interface which defines a \texttt{transform} method. It takes as input some new
data \texttt{X\_test} and yields as output a transformed version of
\texttt{X\_test}. Preprocessing, feature selection, feature extraction and dimensionality reduction
algorithms are all provided as transformers within the library.  In our example,
to standardize the input \texttt{X\_train} to zero mean and unit variance
before fitting the logistic regression estimator,
one would write:
\begin{pythoncode}
from sklearn.preprocessing import StandardScaler

@@

Recent years have witnessed a rising interest in machine learning and data
mining with applications in many fields. With this rise comes a host of machine
learning packages (both open source and proprietary) with which \sklearn
competes. Some of those, including Weka~\citep{hall2009weka} or
Orange~\citep{Demsar2004}, offer and focus on a graphical user interface (GUI)
which allows novices to easily use and apply machine learning algorithms. By
contrast, the target audience of \sklearn is capable of programming, and
therefore we focus on developing a usable and consistent API, rather than expend
effort into creating a GUI\@. In addition, while GUIs are useful tools, they
sometimes make reproducibility difficult in the case of complex workflows
(although those packages usually have developed a GUI for managing complex
tasks).
